% Configuration
\input{includes/config.tex}
%
\begin{document}
%
% Titlepage
\maketitle{Master Thesis}{International Software Systems Science}{Open‐Source Software Discovery and Vulnerability Analysis}{Rajendran, Hari Prashanth}{23.09.2021}
%
% TOCs
\begin{abstract}
In this technology era, most software developers and enterprises are bound to use open-source software components to reduce development efforts. Which also says 96\% of the applications used in enterprises is built through open-source software\cite{Gilad}. These \acs{OSS} components are shared with the help of portals like GitHub and GitLab. The main strength of the \acs{OSS} component, which is highly shareable and reusable, will be the most significant weakness. Due to its rising IT security threats, the security part is still being improved from the beginning of "shared code culture". An unsecured \acs{OSS} component may lead to substantial security threats. Most of the known security issues and threats are registered in vulnerability databases. There are few active vulnerability databases available in the market, and users can search \acs{OSS} components/software in the vulnerability database. 

This thesis builds an \acs{OSS} vulnerability scanning web application to extract and analyse the \acs{OSS} component used inside software projects. At the same time, the scanning takes place on the client-side due to the source code privacy of the user's software project. The automation of extracting the \acs{OSS} components is mandatory because a software project can consist of a lot of \acs{OSS} packages/libraries. The first step is to create an automated solution to extract the \acs{OSS} components. The \acs{OSS} scanner can scan most of the known software projects, and it is also built by considering the scalability of the software projects. The application will analyse the extracted components from the scanner to find the known vulnerability with the \acs{NVD} vulnerability database's help and retrieve all the known vulnerabilities of the \acs{OSS} components found in the project. Finally, the results will be analysed and converted into a simple pdf report to the end-user.
	
\end{abstract}
\newpage
\pagenumbering{Roman}
\tableofcontents
\newpage
\listoffigures
\newpage
\listoftables
\newpage
\lstlistoflistings
\newpage
\fancyhead[LO]{\footnotesize\sc\nouppercase{Abbreviations}}
\input{abbreviations/abbreviations.tex}
\newpage
\fancyhead[LO]{\footnotesize\sc\nouppercase{\leftmark}}
\setcounter{page}{1}
\pagenumbering{arabic}
%
% Insert your chapters here
%
\input{sections/chapter-1.tex}
\newpage
%
\input{sections/chapter-2.tex}
%
\newpage
\input{sections/chapter-3.tex}
%
\newpage
\input{sections/chapter-4.tex}
%
\newpage
\input{sections/chapter-5.tex}
%
\newpage
\input{sections/chapter-6.tex}
%
\newpage
\input{sections/chapter-7.tex}
%
%\newpage
%\input{sections/chapter-8.tex}
%
\newpage
%
% References
\addcontentsline{toc}{section}{References}
\bibliographystyle{alpha}
%
% Insert your bibliography here
\bibliography{bibliography/references}
\newpage
%
% Eigenständigkeitserklärung APO
\makedeclaration{master’s thesis}{23.09.2021}{Hari Prashanth Rajendran}
%
\end{document}
